Exp 2 of 4

### 2016-10-01 experiments/e2/writeup/e2-b-knitr.tex
a messy commit

\documentclass[a4paper,12pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

@@

\clearpage
\section{Get the data}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{# if the file data_processed.Rda already exists then load it, else do data wrangling}
\hlkwa{if} \hlstd{(}\hlkwd{file.exists}\hlstd{(}\hlstr{"data_processed.Rda"}\hlstd{)) \{}
    \hlkwd{load}\hlstd{(}\hlstr{"data_processed.Rda"}\hlstd{)}
\hlstd{\}} \hlkwa{else} \hlstd{\{}
    \hlcom{# declare local variables}
    \hlstd{number_of_valid_subjects} \hlkwb{<-} \hlnum{30}  \hlcom{# = 30}
    \hlstd{number_of_rows} \hlkwb{<-} \hlnum{7680}  \hlcom{# 7680}
    \hlstd{number_of_trials_per_subject} \hlkwb{<-} \hlstd{number_of_rows}\hlopt{/}\hlstd{number_of_valid_subjects}  \hlcom{# = 256}
    \hlcom{# call functions}
    \hlstd{dat} \hlkwb{<-} \hlkwd{gatherData}\hlstd{(number_of_valid_subjects)}  \hlcom{# = 30}
    \hlstd{dat} \hlkwb{<-} \hlkwd{classifyResponses}\hlstd{(dat)}  \hlcom{# classify the response as expected, near, or far}
    \hlstd{dat} \hlkwb{<-} \hlkwd{processData}\hlstd{(dat)}  \hlcom{# remove impossible trials and re-do previous rt measures}
    \hlstd{dd} \hlkwb{<-} \hlkwd{postProcessData}\hlstd{(dat)}
\hlstd{\}}  \hlcom{# end else do data wrangling}
\end{alltt}
\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{names}\hlstd{(dd)}
\end{alltt}
\begin{verbatim}
 [1] "id"                "Subject"           "Trial"             "Condition"        
 [5] "Order"             "Quantity"          "Vagueness"         "Number"           
 [9] "Item"              "discriminability"  "c_Trl"             "s_Trl"            
[13] "c_Itm"             "c_Vag"             "c_Num"             "f_Cnd"            
[17] "c_Ord"             "c_Qty"             "RT"                "RT_log"           
[21] "RT_raw"            "RTprev"            "RTprev_log"        "RTprev_raw"       
[25] "Exp_Num"           "Bline_Num"         "Extr_Num"          "Exp_side"         
[29] "Bline_side"        "Extr_side"         "response_num"      "response_side"    
[33] "response_category" "Left"              "Mid"               "Right"            
[37] "Instruction"       "nchar_instr"      
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{head}\hlstd{(dd)}
\end{alltt}
\begin{verbatim}
        id Subject Trial Condition Order Quantity Vagueness  Number     Item discriminability
1 s01:t001     s01     1         2  RtoL    Small     Crisp Numeric 06:15:24        0.4875000
2 s01:t002     s01     2         1  LtoR    Large     Vague Numeric 16:25:34        0.3123529
3 s01:t003     s01     3         4  LtoR    Small     Crisp  Verbal 26:35:44        0.2308442
4 s01:t004     s01     4         1  RtoL    Large     Vague Numeric 36:45:54        0.1833333
5 s01:t005     s01     5         1  RtoL    Small     Vague Numeric 06:15:24        0.4875000
6 s01:t006     s01     6         3  LtoR    Large     Vague  Verbal 16:25:34        0.3123529
   c_Trl     s_Trl c_Itm c_Vag c_Num f_Cnd c_Ord c_Qty   RT   RT_log RT_raw RTprev RTprev_log
1 -127.5 -1.725186 -0.75  -0.5  -0.5 Cr:Nm   0.5  -0.5 1517 7.324490   1517   1517   7.324490
2 -126.5 -1.711655 -0.25   0.5  -0.5 Vg:Nm  -0.5   0.5 1920 7.560080   1920   1517   7.324490
3 -125.5 -1.698124  0.25  -0.5   0.5 Cr:Vb  -0.5  -0.5 2346 7.760467   2346   1920   7.560080
4 -124.5 -1.684593  0.75   0.5  -0.5 Vg:Nm   0.5   0.5 1773 7.480428   1773   2346   7.760467
5 -123.5 -1.671062 -0.75   0.5  -0.5 Vg:Nm   0.5  -0.5 2556 7.846199   2556   1773   7.480428
6 -122.5 -1.657531 -0.25   0.5   0.5 Vg:Vb  -0.5   0.5 2043 7.622175   2043   2556   7.846199
  RTprev_raw Exp_Num Bline_Num Extr_Num Exp_side Bline_side Extr_side response_num response_side
1       1517       6        15       24    right        mid      left            6         right
2       1517      34        25       16    right        mid      left           25           mid
3       1920      26        35       44     left        mid     right           26          left
4       2346      54        45       36     left        mid     right           45           mid
5       1773       6        15       24    right        mid      left            6         right
6       2556      34        25       16    right        mid      left           34         right
  response_category Left Mid Right                            Instruction nchar_instr
1          expected   24  15     6          Choose the square with 6 dots          29
2        borderline   16  25    34     Choose a square with about 30 dots          34
3          expected   26  35    44 Choose the square with the fewest dots          38
4        borderline   54  45    36     Choose a square with about 50 dots          34
5          expected   24  15     6     Choose a square with about 10 dots          34
6          expected   16  25    34         Choose a square with many dots          30
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{summary}\hlstd{(dd)}
\end{alltt}
\begin{verbatim}
        id          Subject         Trial         Condition    Order       Quantity    Vagueness   
 s01:t001:   1   s01    : 256   Min.   :  1.0   Min.   :1.0   LtoR:3838   Small:3840   Crisp:3840  
 s01:t002:   1   s02    : 256   1st Qu.: 65.0   1st Qu.:2.0   RtoL:3839   Large:3837   Vague:3837  
 s01:t003:   1   s03    : 256   Median :129.0   Median :3.0                                        
 s01:t004:   1   s04    : 256   Mean   :128.5   Mean   :2.5                                        
 s01:t005:   1   s05    : 256   3rd Qu.:193.0   3rd Qu.:4.0                                        
 s01:t006:   1   s06    : 256   Max.   :256.0   Max.   :4.0                                        
 (Other) :7671   (Other):6141                                                                      
     Number           Item      discriminability     c_Trl                s_Trl           
 Numeric:3838   06:15:24:1919   Min.   :0.1833   Min.   :-127.50000   Min.   :-1.7251858  
 Verbal :3839   16:25:34:1919   1st Qu.:0.2308   1st Qu.: -63.50000   1st Qu.:-0.8592102  
                26:35:44:1920   Median :0.2308   Median :   0.50000   Median : 0.0067654  
                36:45:54:1919   Mean   :0.3035   Mean   :   0.02377   Mean   : 0.0003217  
                                3rd Qu.:0.3124   3rd Qu.:  64.50000   3rd Qu.: 0.8727411  
                                Max.   :0.4875   Max.   : 127.50000   Max.   : 1.7251858

     c_Itm               c_Vag                c_Num             f_Cnd          c_Ord          
 Min.   :-7.50e-01   Min.   :-0.5000000   Min.   :-5.00e-01   Vg:Nm:1918   Min.   :-5.00e-01  
 1st Qu.:-2.50e-01   1st Qu.:-0.5000000   1st Qu.:-5.00e-01   Cr:Nm:1920   1st Qu.:-5.00e-01  
 Median : 2.50e-01   Median :-0.5000000   Median : 5.00e-01   Vg:Vb:1919   Median : 5.00e-01  
 Mean   : 3.26e-05   Mean   :-0.0001954   Mean   : 6.51e-05   Cr:Vb:1920   Mean   : 6.51e-05  
 3rd Qu.: 2.50e-01   3rd Qu.: 0.5000000   3rd Qu.: 5.00e-01                3rd Qu.: 5.00e-01  
 Max.   : 7.50e-01   Max.   : 0.5000000   Max.   : 5.00e-01                Max.   : 5.00e-01

     c_Qty                  RT            RT_log           RT_raw          RTprev     
 Min.   :-0.5000000   Min.   :  445   Min.   : 6.098   Min.   :  445   Min.   :  445  
 1st Qu.:-0.5000000   1st Qu.: 1240   1st Qu.: 7.123   1st Qu.: 1240   1st Qu.: 1240  
 Median :-0.5000000   Median : 1727   Median : 7.454   Median : 1727   Median : 1727  
 Mean   :-0.0001954   Mean   : 2840   Mean   : 7.595   Mean   : 2840   Mean   : 2835  
 3rd Qu.: 0.5000000   3rd Qu.: 2699   3rd Qu.: 7.901   3rd Qu.: 2699   3rd Qu.: 2697  
 Max.   : 0.5000000   Max.   :42685   Max.   :10.662   Max.   :42685   Max.   :42685

   RTprev_log       RTprev_raw       Exp_Num     Bline_Num     Extr_Num    Exp_side        
 Min.   : 6.098   Min.   :  445   Min.   : 6   Min.   :15   Min.   : 6   Length:7677       
 1st Qu.: 7.123   1st Qu.: 1240   1st Qu.:16   1st Qu.:25   1st Qu.:24   Class :character  
 Median : 7.454   Median : 1727   Median :26   Median :35   Median :34   Mode  :character  
 Mean   : 7.594   Mean   : 2835   Mean   :30   Mean   :30   Mean   :30                     
 3rd Qu.: 7.900   3rd Qu.: 2697   3rd Qu.:36   3rd Qu.:35   3rd Qu.:44                     
 Max.   :10.662   Max.   :42685   Max.   :54   Max.   :45   Max.   :54

  Bline_side         Extr_side          response_num   response_side  response_category
 Length:7677        Length:7677        Min.   : 6.00   left :3215    borderline:1274   
 Class :character   Class :character   1st Qu.:24.00   mid  :1274    expected  :6108   
 Mode  :character   Mode  :character   Median :34.00   right:3188    extreme   : 295   
                                       Mean   :30.87                                   
                                       3rd Qu.:44.00                                   
                                       Max.   :54.00

      Left         Mid         Right                                    Instruction  
 Min.   : 6   Min.   :15   Min.   : 6   Choose a square with few dots         : 960  
 1st Qu.:24   1st Qu.:25   1st Qu.:24   Choose the square with the fewest dots: 960  
 Median :34   Median :35   Median :26   Choose the square with the most dots  : 960  
 Mean   :30   Mean   :30   Mean   :30   Choose a square with many dots        : 959  
 3rd Qu.:44   3rd Qu.:35   3rd Qu.:36   Choose a square with about 30 dots    : 480  
 Max.   :54   Max.   :45   Max.   :54   Choose a square with about 40 dots    : 480  
                                        (Other)                               :2878  
  nchar_instr   
 Min.   :29.00  
 1st Qu.:30.00  
 Median :30.00  
 Mean   :32.59  
 3rd Qu.:36.00  
 Max.   :38.00

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{str}\hlstd{(dd)}
\end{alltt}
\begin{verbatim}
'data.frame':	7677 obs. of  38 variables:
 $ id               : Factor w/ 7680 levels "s01:t001","s01:t002",..: 1 2 3 4 5 6 7 8 9 10 ...
 $ Subject          : Factor w/ 30 levels "s01","s02","s03",..: 1 1 1 1 1 1 1 1 1 1 ...
 $ Trial            : int  1 2 3 4 5 6 7 8 9 10 ...
 $ Condition        : int  2 1 4 1 1 3 3 4 4 2 ...
 $ Order            : Factor w/ 2 levels "LtoR","RtoL": 2 1 1 2 2 1 2 2 1 2 ...
 $ Quantity         : Factor w/ 2 levels "Small","Large": 1 2 1 2 1 2 1 1 2 2 ...
 $ Vagueness        : Factor w/ 2 levels "Crisp","Vague": 1 2 1 2 2 2 2 1 1 1 ...
 $ Number           : Factor w/ 2 levels "Numeric","Verbal": 1 1 2 1 1 2 2 2 2 1 ...
 $ Item             : Factor w/ 4 levels "06:15:24","16:25:34",..: 1 2 3 4 1 2 3 4 1 2 ...
 $ discriminability : num  0.487 0.312 0.231 0.183 0.487 ...
 $ c_Trl            : num  -128 -126 -126 -124 -124 ...
 $ s_Trl            : num  -1.73 -1.71 -1.7 -1.68 -1.67 ...
 $ c_Itm            : num  -0.75 -0.25 0.25 0.75 -0.75 -0.25 0.25 0.75 -0.75 -0.25 ...
 $ c_Vag            : num  -0.5 0.5 -0.5 0.5 0.5 0.5 0.5 -0.5 -0.5 -0.5 ...
 $ c_Num            : num  -0.5 -0.5 0.5 -0.5 -0.5 0.5 0.5 0.5 0.5 -0.5 ...
 $ f_Cnd            : Factor w/ 4 levels "Vg:Nm","Cr:Nm",..: 2 1 4 1 1 3 3 4 4 2 ...
 $ c_Ord            : num  0.5 -0.5 -0.5 0.5 0.5 -0.5 0.5 0.5 -0.5 0.5 ...
 $ c_Qty            : num  -0.5 0.5 -0.5 0.5 -0.5 0.5 -0.5 -0.5 0.5 0.5 ...
 $ RT               : int  1517 1920 2346 1773 2556 2043 2384 3078 1760 2218 ...
 $ RT_log           : num  7.32 7.56 7.76 7.48 7.85 ...
 $ RT_raw           : int  1517 1920 2346 1773 2556 2043 2384 3078 1760 2218 ...
 $ RTprev           : int  1517 1517 1920 2346 1773 2556 2043 2384 3078 1760 ...
 $ RTprev_log       : num  7.32 7.32 7.56 7.76 7.48 ...
 $ RTprev_raw       : int  1517 1517 1920 2346 1773 2556 2043 2384 3078 1760 ...
 $ Exp_Num          : num  6 34 26 54 6 34 26 36 24 34 ...
 $ Bline_Num        : num  15 25 35 45 15 25 35 45 15 25 ...
 $ Extr_Num         : num  24 16 44 36 24 16 44 54 6 16 ...
 $ Exp_side         : chr  "right" "right" "left" "left" ...
 $ Bline_side       : chr  "mid" "mid" "mid" "mid" ...
 $ Extr_side        : chr  "left" "left" "right" "right" ...
 $ response_num     : int  6 25 26 45 6 34 26 36 24 25 ...
 $ response_side    : Factor w/ 3 levels "left","mid","right": 3 2 1 2 3 3 3 3 3 2 ...
 $ response_category: Factor w/ 3 levels "borderline","expected",..: 2 1 2 1 2 2 2 2 2 1 ...
 $ Left             : int  24 16 26 54 24 16 44 54 6 34 ...
 $ Mid              : int  15 25 35 45 15 25 35 45 15 25 ...
 $ Right            : int  6 34 44 36 6 34 26 36 24 16 ...
 $ Instruction      : Factor w/ 17 levels "Choose a square with about 10 dots",..: 15 3 16 5 1 7 6 16 17 11 ...
 $ nchar_instr      : int  29 34 38 34 34 30 29 38 36 30 ...
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

>>>>

\documentclass[a4paper,12pt,twoside]{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

@@

\section{Get the data}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{source}\hlstd{(}\hlstr{"e2-preprocessing.R"}\hlstd{)}
\hlkwa{if} \hlstd{(}\hlopt{!}\hlkwd{file.exists}\hlstd{(}\hlstr{"e2-b-data.txt"}\hlstd{)) \{}
    \hlstd{dat} \hlkwb{<-} \hlkwd{gatherData}\hlstd{()}
    \hlstd{dat} \hlkwb{<-} \hlkwd{declareImpossibleRT}\hlstd{(dat)}
    \hlstd{dat} \hlkwb{<-} \hlkwd{removeImpossibleTrials}\hlstd{(dat)}
    \hlstd{dat} \hlkwb{<-} \hlkwd{subset}\hlstd{(dat,} \hlkwc{select} \hlstd{=} \hlkwd{c}\hlstd{(Subject, Trial, Item, discriminability, Instruction, nchar_instr, Vagueness,}
        \hlstd{Number, Order, Quantity, c_Vag, c_Num, c_Ord, c_Qty, NaType, response_category, isBorderline,}
        \hlstd{RT))}
    \hlkwd{write.table}\hlstd{(dat,} \hlkwc{file} \hlstd{=} \hlstr{"e2-b-data.txt"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{"\textbackslash{}t"}\hlstd{,} \hlkwc{quote} \hlstd{=} \hlnum{FALSE}\hlstd{)}
\hlstd{\}}
\hlstd{dat} \hlkwb{<-} \hlkwd{read.delim}\hlstd{(}\hlstr{"e2-b-data.txt"}\hlstd{)}
\hlstd{dd} \hlkwb{<-} \hlkwd{read.delim}\hlstd{(}\hlstr{"e2-b-data.txt"}\hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{names}\hlstd{(dd)}
\end{alltt}
\begin{verbatim}
 [1] "Subject"           "Trial"             "Item"              "discriminability" 
 [5] "Instruction"       "nchar_instr"       "Vagueness"         "Number"           
 [9] "Order"             "Quantity"          "c_Vag"             "c_Num"            
[13] "c_Ord"             "c_Qty"             "NaType"            "response_category"
[17] "isBorderline"      "RT"               
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{head}\hlstd{(dd)}
\end{alltt}
\begin{verbatim}
  Subject Trial     Item discriminability                            Instruction nchar_instr
1     s01     1 06:15:24        0.4875000          Choose the square with 6 dots          29
2     s01     2 16:25:34        0.3123529     Choose a square with about 30 dots          34
3     s01     3 26:35:44        0.2308442 Choose the square with the fewest dots          38
4     s01     4 36:45:54        0.1833333     Choose a square with about 50 dots          34
5     s01     5 06:15:24        0.4875000     Choose a square with about 10 dots          34
6     s01     6 16:25:34        0.3123529         Choose a square with many dots          30
  Vagueness  Number Order Quantity c_Vag c_Num c_Ord c_Qty      NaType response_category
1     Crisp Numeric  RtoL    Small  -0.5  -0.5   0.5  -0.5 valid_trial          expected
2     Vague Numeric  LtoR    Large   0.5  -0.5  -0.5   0.5 valid_trial        borderline
3     Crisp  Verbal  LtoR    Small  -0.5   0.5  -0.5  -0.5 valid_trial          expected
4     Vague Numeric  RtoL    Large   0.5  -0.5   0.5   0.5 valid_trial        borderline
5     Vague Numeric  RtoL    Small   0.5  -0.5   0.5  -0.5 valid_trial          expected
6     Vague  Verbal  LtoR    Large   0.5   0.5  -0.5   0.5 valid_trial          expected
  isBorderline   RT
1        FALSE 1517
2         TRUE 1920
3        FALSE 2346
4         TRUE 1773
5        FALSE 2556
6        FALSE 2043
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{summary}\hlstd{(dd)}
\end{alltt}
\begin{verbatim}
    Subject         Trial             Item      discriminability
 s01    : 256   Min.   :  1.0   06:15:24:1919   Min.   :0.1833  
 s02    : 256   1st Qu.: 65.0   16:25:34:1919   1st Qu.:0.2308  
 s03    : 256   Median :129.0   26:35:44:1920   Median :0.2308  
 s04    : 256   Mean   :128.5   36:45:54:1919   Mean   :0.3035  
 s05    : 256   3rd Qu.:193.0                   3rd Qu.:0.3124  
 s06    : 256   Max.   :256.0                   Max.   :0.4875  
 (Other):6141                                                   
                                 Instruction    nchar_instr    Vagueness        Number    
 Choose a square with few dots         : 960   Min.   :29.00   Crisp:3840   Numeric:3838  
 Choose the square with the fewest dots: 960   1st Qu.:30.00   Vague:3837   Verbal :3839  
 Choose the square with the most dots  : 960   Median :30.00                              
 Choose a square with many dots        : 959   Mean   :32.59                              
 Choose a square with about 30 dots    : 480   3rd Qu.:36.00                              
 Choose a square with about 40 dots    : 480   Max.   :38.00                              
 (Other)                               :2878                                              
  Order       Quantity        c_Vag                c_Num               c_Ord          
 LtoR:3838   Large:3837   Min.   :-0.5000000   Min.   :-5.00e-01   Min.   :-5.00e-01  
 RtoL:3839   Small:3840   1st Qu.:-0.5000000   1st Qu.:-5.00e-01   1st Qu.:-5.00e-01  
                          Median :-0.5000000   Median : 5.00e-01   Median : 5.00e-01  
                          Mean   :-0.0001954   Mean   : 6.51e-05   Mean   : 6.51e-05  
                          3rd Qu.: 0.5000000   3rd Qu.: 5.00e-01   3rd Qu.: 5.00e-01  
                          Max.   : 0.5000000   Max.   : 5.00e-01   Max.   : 5.00e-01

     c_Qty                    NaType      response_category isBorderline          RT       
 Min.   :-0.5000000   valid_trial:7677   borderline:1274    Mode :logical   Min.   :  445  
 1st Qu.:-0.5000000                      expected  :6108    FALSE:6403      1st Qu.: 1240  
 Median :-0.5000000                      extreme   : 295    TRUE :1274      Median : 1727  
 Mean   :-0.0001954                                         NA's :0         Mean   : 2840  
 3rd Qu.: 0.5000000                                                         3rd Qu.: 2699  
 Max.   : 0.5000000                                                         Max.   :42685

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{str}\hlstd{(dd)}
\end{alltt}
\begin{verbatim}
'data.frame':	7677 obs. of  18 variables:
 $ Subject          : Factor w/ 30 levels "s01","s02","s03",..: 1 1 1 1 1 1 1 1 1 1 ...
 $ Trial            : int  1 2 3 4 5 6 7 8 9 10 ...
 $ Item             : Factor w/ 4 levels "06:15:24","16:25:34",..: 1 2 3 4 1 2 3 4 1 2 ...
 $ discriminability : num  0.487 0.312 0.231 0.183 0.487 ...
 $ Instruction      : Factor w/ 17 levels "Choose a square with about 10 dots",..: 15 3 16 5 1 7 6 16 17 11 ...
 $ nchar_instr      : int  29 34 38 34 34 30 29 38 36 30 ...
 $ Vagueness        : Factor w/ 2 levels "Crisp","Vague": 1 2 1 2 2 2 2 1 1 1 ...
 $ Number           : Factor w/ 2 levels "Numeric","Verbal": 1 1 2 1 1 2 2 2 2 1 ...
 $ Order            : Factor w/ 2 levels "LtoR","RtoL": 2 1 1 2 2 1 2 2 1 2 ...
 $ Quantity         : Factor w/ 2 levels "Large","Small": 2 1 2 1 2 1 2 2 1 1 ...
 $ c_Vag            : num  -0.5 0.5 -0.5 0.5 0.5 0.5 0.5 -0.5 -0.5 -0.5 ...
 $ c_Num            : num  -0.5 -0.5 0.5 -0.5 -0.5 0.5 0.5 0.5 0.5 -0.5 ...
 $ c_Ord            : num  0.5 -0.5 -0.5 0.5 0.5 -0.5 0.5 0.5 -0.5 0.5 ...
 $ c_Qty            : num  -0.5 0.5 -0.5 0.5 -0.5 0.5 -0.5 -0.5 0.5 0.5 ...
 $ NaType           : Factor w/ 1 level "valid_trial": 1 1 1 1 1 1 1 1 1 1 ...
 $ response_category: Factor w/ 3 levels "borderline","expected",..: 2 1 2 1 2 2 2 2 2 1 ...
 $ isBorderline     : logi  FALSE TRUE FALSE TRUE FALSE FALSE ...
 $ RT               : int  1517 1920 2346 1773 2556 2043 2384 3078 1760 2218 ...
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\clearpage
\subsection{Consider using log RT}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in `*tmp*`[[j]]: subscript out of bounds}}

{\ttfamily\noindent\color{warningcolor}{Warning in mean.default(dat\_transforms[dat\_transforms\$dfSubset == k \& dat\_transforms\$RTtype == : argument is not numeric or logical: returning NA}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in `[<-.data.frame`(`*tmp*`, dat\_transforms\$dfSubset == k \& dat\_transforms\$RTtype == : replacement has length zero}}\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error: measure variables not found in data: RT\_log, RT\_raw}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in ggplot(temp, aes(time, colour = RTtype)): object 'temp' not found}}\end{kframe}
\end{knitrout}

\clearpage
\subsection{How logging RT affects the distribution}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\color{warningcolor}{Warning in readChar(con, 5L, useBytes = TRUE): cannot open compressed file 'data\_processed.Rda', probable reason 'No such file or directory'}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in readChar(con, 5L, useBytes = TRUE): cannot open the connection}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error: measure variables not found in data: RT\_log, RT\_raw}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in ggplot(subdata): object 'subdata' not found}}\end{kframe}
\end{knitrout}

\clearpage
\subsection{Identify fast and slow subjects and items}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\color{warningcolor}{Warning in mean.default(dd\$RT\_log): argument is not numeric or logical: returning NA}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in mean(RT\_log): object 'RT\_log' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in subs\$level = 1:30: object 'subs' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in factor(subs\$effect, levels = c("{}subject"{}, "{}discriminability"{})): object 'subs' not found}}

{\ttfamily\noindent\color{warningcolor}{Warning in mean.default(dd\$RT\_log): argument is not numeric or logical: returning NA}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in mean(RT\_log): object 'RT\_log' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in factor(itms\$effect, levels = c("{}subject"{}, "{}discriminability"{})): object 'itms' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in rbind(subs, itms): object 'subs' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in factor(si\$effect, levels = c("{}subject"{}, "{}discriminability"{})): object 'si' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in unique(si\$emean): object 'si' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in eval(substitute(groups), data, environment(x)): object 'si' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in inherits(obj1, "{}trellis"{}): object 'my1' not found}}\end{kframe}
\end{knitrout}

\clearpage
\subsection{Plot main effects in both transformations}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error: measure variables not found in data: RT\_raw}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in reshape2::melt(tempraw, id.vars = c("{}transformation"{}, "{}score"{}), : object 'tempraw' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error: measure variables not found in data: RT\_log}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in reshape2::melt(templog, id.vars = c("{}transformation"{}, "{}score"{}), : object 'templog' not found}}\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in ggplot(tempraw2, aes(y = score, x = level, group = 1, col = effect)): object 'tempraw2' not found}}\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in ggplot(templog2, aes(y = score, x = level, group = 1, col = effect)): object 'templog2' not found}}\end{kframe}
\end{knitrout}

\clearpage
\subsection{Main effects in log RT over discriminability}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in `[.data.frame`(xx, , col): undefined columns selected}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in names(nrts)[5] <- "{}Levels"{}: object 'nrts' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in `[.data.frame`(xx, , col): undefined columns selected}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in names(orts)[5] <- "{}Levels"{}: object 'orts' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in `[.data.frame`(xx, , col): undefined columns selected}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in names(qrts)[5] <- "{}Levels"{}: object 'qrts' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in `[.data.frame`(xx, , col): undefined columns selected}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in names(vrts)[5] <- "{}Levels"{}: object 'vrts' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in rbind(nrts, orts, qrts, vrts): object 'nrts' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{Error in eval(expr, envir, enclos): object 'rts' not found}}
